Algebraic File Synchronization: Adequacy and Completeness

### 2018-07-02 p2/axioms.tex
Proofs for the rules

\begin{mydef}[Construction and destruction pairs]
A pair of commands on nodes $\nn$ and $n$ where $\nn=\parentf{n}$
is a \emph{construction pair} if the input and output types match
one of the following patterns:
   \begin{align*}
            \cbda{\nn}&\cc  \cbfa{n} \\
            \cbda{\nn}&\cc  \cbda{n} \\
            \cfda{\nn}&\cc  \caaa{\empt}{\valff}{n} \\
            \cfda{\nn}&\cc  \cbda{n}
   \end{align*}
The pair is a \emph{destruction pair} if the types match one of the following:
   \begin{align*}
            \cfba{n}&\cc  \cdba{\nn} \\
            \cfba{n}&\cc  \caaa{\vald}{\valff}{\nn} \\
            \cdba{n}&\cc  \cdba{\nn} \\
            \cdba{n}&\cc  \cdfa{\nn}
   \end{align*}
\end{mydef}

@@

\Cref{rules_lemma} summarizes the basic properties of command pairs.
The claims listed are named \emph{\namecref{ax_separate_commute}}
as they can also be interpreted as inference rules in a pure
algebraic treatment of filesystem synchronization.
TODO elaborates this approach.

@@

\item\mlabel{ax_same_emptyseq}
Otherwise commands on the same node are extended by an empty sequence if their outer types represent
an assertion command:
$\cxynv\cc\czwnv \eqext \emptyseq$ where $[y]=[z]$, and $\cxw=\cbb$ 
or $\cxw=\cdd$.

\item\mlabel{ax_same_singlec}
All other command pairs on the same node are equivalent to a single command:
$\cxynv\cc \czwnv \equiv \cxwnv$ where $[y]=[z]$ and $\cxw\neq\cbb$ and $\cxw\neq\cdd$.

% TODO Renumber rules in script

\item\mlabel{ax_directchild_breaks}
Commands on a parent and a child node break every filesystem
if the pair is not a construction pair
and the commands do not simply assert a directory at the parent
or an empty node at the child:
$\cxynnv\cc\czwnv \equiv \cbrk$ where $\nn=\parent(n)$ and $\cxy\neq\cdd$ and $\czw\neq\cbb$.

\item\mlabel{ax_directparent_breaks}
Commands on a child and parent node break every filesystem
if the pair is not a destruction pair
and the commands do not simply assert an empty node at the child
or a directory at the parent:
$\cxynv\cc\czwnnv \equiv \cbrk$ where $\parent(n)=\nn$ and $\cxy\neq\cbb$ and $\czw\neq\cdd$.

@@

For \cref{ax_distantrel_breaks}, we also provide a simple proof.
Suppose $\cxynnv$ and $\czwnv$ satisfy the conditions in the \namecref{ax_distantrel_breaks},
and there if an $\FS$ for which $(\cxynnv\cc\czwnv)\aFS\neq\fsbroken$.
If $\czw\neq\cbb$, then either $\FS(n)\neq\empty$ or $\czwnv\aFS(n)\neq\empty$,
and therefore $\FS(\parentf{n})$ must be a directory for the filesystem to satisfy
the tree property at all times.
However, from $\cxy\neq\cdd$ we also know that either $\FS(\nn)$ 
(before applying $\cxynv$) or $\cxynv\aFS(\nn)$ (after applying $\cxynv$)
is not a directory. Depending on which is true, we have a point in the sequence
of applying the commands where the filesystem cannot satify the tree property
and therefore becomes broken as $\parentf{n}$, a descendant of $\nn$, contains
a directory and so must all its ancestors.

>>>>

\begin{mydef}[Construction and destruction pairs]
A pair of commands on nodes $\pn$ and $n$
is a \emph{construction pair} if the input and output types match
one of the following patterns:
   \begin{align*}
            \cbda{\pn}&\cc  \cbfa{n} \\
            \cbda{\pn}&\cc  \cbda{n} \\
            \cfda{\pn}&\cc  \caaa{\empt}{\valff}{n} \\
            \cfda{\pn}&\cc  \cbda{n}
   \end{align*}
The pair is a \emph{destruction pair} if the types match one of the following:
   \begin{align*}
            \cfba{n}&\cc  \cdba{\pn} \\
            \cfba{n}&\cc  \caaa{\vald}{\valff}{\pn} \\
            \cdba{n}&\cc  \cdba{\pn} \\
            \cdba{n}&\cc  \cdfa{\pn}
   \end{align*}
\end{mydef}

@@

\Cref{rules_lemma} summarizes the basic properties of command pairs.
The claims listed are named \emph{\namecrefs{ax_separate_commute}}
as they can also be interpreted as inference rules in a pure
algebraic treatment of filesystem synchronization.
TODO elaborates this approach.

@@

\item\mlabel{ax_same_emptyseq}
Commands on the same node are extended by an empty sequence if their types are compatible,
and their outer types represent an assertion command:
$\cxynv\cc\czwnv \eqext \emptyseq$ where $[y]=[z]$; and 
$[x]=[\empt]$ and $[w]=[\empt]$,
or $[x]=[\vald]$ and $[w]=[\vald]$.

\item\mlabel{ax_same_singlec}
Command pairs on the same node are equivalent to a single command if their types are compatible,
and their outer types do not represent an assertion command:
$\cxynv\cc \czwnv \equiv \cxwnv$ where $[y]=[z]$; and
neither $[x]=[\empt]$ and $[w]=[\empt]$,
nor $[x]=[\vald]$ and $[w]=[\vald]$.

\item\mlabel{ax_directchild_breaks}
Commands on a parent and a child node break every filesystem
if the pair is not a construction pair
and the commands do not simply assert a directory at the parent
or an empty node at the child:
$\cxynnv\cc\czwnv \equiv \cbrk$ where $\cxy\neq\cdd$ and $\czw\neq\cbb$.

\item\mlabel{ax_directparent_breaks}
Commands on a child and parent node break every filesystem
if the pair is not a destruction pair
and the commands do not simply assert an empty node at the child
or a directory at the parent:
$\cxynv\cc\czwnnv \equiv \cbrk$ where $\cxy\neq\cbb$ and $\czw\neq\cdd$.

@@

For \cref{ax_distantrel_breaks}, we also provide a simple proof.
Suppose $\cxynnv$ and $\czwnv$ satisfy the conditions in the \namecref{ax_distantrel_breaks},
and there is an $\FS$ for which $(\cxynnv\cc\czwnv)\aFS\neq\fsbroken$.
If $\czw\neq\cbb$, then either $\FS(n)\neq\empty$ or $\czwnv\aFS(n)\neq\empty$,
and therefore $\FS(\parentf{n})$ must be a directory for the filesystem to satisfy
the tree property at all times.
However, from $\cxy\neq\cdd$ we also know that either $\FS(\nn)$ 
(before applying $\cxynv$) or $\cxynv\aFS(\nn)$ (after applying $\cxynv$)
is not a directory. Depending on which is true, we have a point in the sequence
of applying the commands where the filesystem cannot satify the tree property
and therefore becomes broken as $\parentf{n}$, a descendant of $\nn$, contains
a directory and so must all its ancestors.
